\documentclass[11pt]{scrartcl}

\title{\textbf{Project Evaluation}}
\subtitle{Evaluation of Software Projects}
\author{Daniel Izquierdo-Cortázar}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}

\section{Exercise}

Describe 5 Mail client requirements.

\begin{itemize}
    \item Multibrowser Web ClientCliente (browser compliant) - We want a Saas mail client to give us access through any channel, any browser.
    \item FLOSS License - We need a FLOOS license first of all; to not depend on outside companies for maintenance, adaptability and software upgrades.
    \item Good community supporting - We want to choose a healthy software not an abandoned one. The community can show their health, viability, importance of the project and the interest aroused.
    \item GUI - It's very  imporant, is a need to have a good GUI which brings together all kinds of users, from technicians to who are not familiar with computers.
    \item Developed through a language known by the company - Due to the immediacy of implementation.
\end{itemize}

\section{GQM: Goals Questions Metrics}

\section{ISO-9126}

You have to pay to access it, nonsense. Here's a summary of the six most important attributes defends in the ISO:
\begin{itemize}
    \item Functionality.
    \item Reliability.
    \item Usability (Ergonomía).
    \item Efficiency.
    \item Maintainability. Estabilidad, test, etc...
    \item Portability.
\end{itemize}

\subsection{Functionality}

Definition; % TBC

\subsection{Realiability}

\begin{itemize}
    \item Maturity.
    \item Fault tolerance.
    \item Recoverability.
    \item Realiability Compliance.
\end{itemize}

\subsection{Usability definition}

What and when ?

% TBC

\end{document}
