\documentclass[11pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}

\title{\textbf{Project Evaluation}}
\subtitle{Define analysis metrics}
\author{Daniel Izquierdo-Cortázar}
\date{\today}

\begin{document}

\maketitle

\newpage

\tableofcontents

\newpage

\section{Introducción}

Source Code Management.

Necesidad de implantar un control de versiones en la empresa debido a la facilidad que aporta a nivel del trabajo en equipo liberándonos de la facilidad de perder información que conlleva el uso de un directorio compartido.

Facilitando el trabajo en grupo impidiendo el intebloqueo y la pérdida de información.

\subsection{Technical Reasons}

Ricardo:
\begin{itemize}
    \item GUI Management Tools.
    \item Integration with IDEs.
    \item Mature and Stable versions.
    \item Lower learning curve.
    \item Success cases.
    \item License.
    \item Backup and restore.
    \item Migration guide.
    \item fork easily.
\end{itemize}

Jesús:
\begin{itemize}
    \item Web access
    \item Low learning curve
    \item User access policy/management
    \item API.
    \item Downloading specific parts of the source code tree
    \item Non-technical users.
\end{itemize}

Johnattan:
\begin{itemize}
    \item Open source
    \item Backup and restore.
    \item Casos de éxito
    \item Open access (web accoess)
    \item Partially technical profiles (some of them translators)
    \item Easy learning
    \item Offline work
\end{itemize}

Ilias:
\begin{itemize}
    \item Multiplataforma
    \item Usability
    \item API (easy to hook from some BTS)
    \item Documentation
\end{itemize}

Common:
\begin{itemize}

    \item Initial Analysis
        \begin{itemize}
            \item License.
        \end{itemize}

    \item Functionality
        \begin{itemize}
            \item UI 
            \item Backup and restore (restore cost estimation or revert actions)
            \item Profile management
            \item Cheap forks
        \end{itemize}

    \item Usabilidad
        \begin{itemize}
            \item UI
        \end{itemize}
    
    \item Robustness
        \begin{itemize}
            \item Multiplatform
            \item Mature and stable version
        \end{itemize}

    \item Development
        \begin{itemize}
            \item API has two different clients:
            \begin{itemize}
                \item C: http://subversion.apache.org/docs/api/latest/ 
                \item Java: http://subversion.apache.org/docs/javahl/latest/
            \end{itemize}
            \item Documentation
        \end{itemize}

\end{itemize}


\subsection{Project's introduction}
\subsection{DAFO (optional)}

Si está soportado, hay una empresa detrás o una comunidad.

\section{Methodology}

Deadline 20-12-2012

\subsection{Evaluation guidelines(quality models/ad hoc models)}
\subsection{Toolset}
\subsection{Data sources}

\begin{itemize}
    \item Website - http://subversion.apache.org/
    \item Source code management system - svn co http://svn.apache.org/repos/asf/subversion/trunk subversion
    \item Releases - http://subversion.apache.org/packages.html
    \item Wikis - http://wiki.apache.org/subversion/
    \item Documentation - http://subversion.apache.org/docs/
    \item Mailing lists -http://subversion.apache.org/mailing-lists.html
    \item Bug tracking system - http://subversion.tigris.org/issue-tracker.html
    \item Irc channel - IRC on channel \#svn on irc.freenode.net
\end{itemize}

\subsection{Update Data Sources}

Bash instructions:

\begin{quote}
    mysql -u root -padmin
\end{quote}

MySQL console:

\begin{quote}
    drop database svn\_scm\_log;
    create database svn\_scm\_log;
    exit
\end{quote}

Bash instructions:

\begin{quote}
    cd ~/projects/svn/subversion
    svn co http://svn.apache.org/repos/asf/subversion/trunk subversion
    cvsanaly2 --db-database svn\_scm\_log --db-user root --db-password admin --db-driver mysql
    mysqldump -u root -padmin svn\_scm\_log > svn\_scm\_log.mysql
\end{quote}

\section{Analysis}

Evaluación de las métricas elegidas.
Deadline 04-01-2013

\section{Results}

Mostrar los resultados.

\section{Conclusions}

\section{Further work}

Resumen, que posibilidades se han dejado fuera y futuribles.
TODO: maillist, bugtracker, standards, foundation, uses, succed.

\section{Deadlines}

\begin{itemize}
    \item 20th Dec - Methodology (evaluation guidelines)
    \item 4th Jan - Analysis (to be shared with others)
    \item 17th Jan - Final deadline.
\end{itemize}

\section{TODOs}

Definir atributos principal y definición de las métricas.

\end{document}
